\cvsection{Experience}
\begin{cventries}
%cook
\cventry
  {Concordia Language Villages, El Lago Del Bosque}
  {Village Cook}
  {Bemidji, MN}
  {July-August 2016}
  {
    \begin{cvitems}
      \item {Worked under the head chef fixing daily meals for campers and
    washing dishes.}
    \end{cvitems}
  }

  %counselor
  \cventry
    {Concordia Language Villages, El Lago Del Bosque}
    {Camp Counselor}
    {Bemidji, MN}
    {July-August 2017}
    {
      \begin{cvitems}
        \item {Worked under Diane Tess as a Spanish immersion camp counselor, teaching children aged 6-18 Spanish conversational skills, and cultural knowledge.}
      \end{cvitems}
    }

  %frc programmer
  \cventry
    {First Robotics Competition, Team 6002}
    {Robot Programmer}
    {Kalamazoo, MI}
    {Oct. 2015 - May 2016}
    {
      \begin{cvitems}
        \item {Wrote Java code for the robot’s basic abilities and autonomous mode.}
      \end{cvitems}
    }

  %volunteer at animal shelter
  \cventry
    {Poweshiek Animal League Shelter}
    {Volunteer}
    {Grinnell, IA}
    {Sep. 2016 - Current}
    {
      \begin{cvitems}
        \item {Cleaned, cared for, and socialized cats and their environment.}
      \end{cvitems}
    }

  %MAP project
  \cventry
    {Undergrad Research Project, Image Synthesis for Machine Learning}
    {Research Assistant}
    {Grinnell, IA}
    {June-August 2018}
    {
      \begin{cvitems}
        \item {Developed a program to generate synthetic training data for a text recognizing CNN.}
        \item{See code at https://github.com/niehusst/MapTextSynthesizer}
      \end{cvitems}
    }

  %Captain of grinnell ultimate team
  \cventry
    {Grinnelliphants Ultimate Frisbee}
    {Team Captain}
    {Grinnell, IA}
    {August 2018 - May 2019}
    {
      \begin{cvitems}
        \item {Gained experience as a teacher and leader.}
      \end{cvitems}
    }

  %grammiegram
  \cventry
    {The GrammieGram Company}
    {Full Stack Developer}
    {Grinnell, IA}
    {April 2018 - Current}
    {
      \begin{cvitems}
        \item {Developed the backend for user preferences}
        \item {Constructed and maintained unit testing for the majority of the web app}
        \item {Designed frontend UI for the contact management page}
        \item {Gained significant experience working with a team using version control}
      \end{cvitems}
    }

  %member of appdev grinnell
  \cventry
    {AppDev Grinnell}
    {Developer}
    {Grinnell, IA}
    {January 2018 - Current}
    {
      \begin{cvitems}
        \item {Worked on the _____ app. Find it on the play store?}
      \end{cvitems}
    }

\end{cventries}
